Proposal

### 2022-06-10 proposal/proposal2.qmd
renamed proposal and changed analysis section

```{r eda-age}
#| warning: false
#Age
ggplot(abortion_data, aes(x = age)) +
  geom_histogram(binwidth = 1) + 
  labs(title = "Histogram of age")
#ggplot(abortion_data, aes(group = age, y = aj)) +
  #geom_density() try to group together
```

```{r eda-college}
#| warning: false
# College education
ggplot(abortion_data, aes(x = collegeed)) +
  geom_histogram() + 
  labs(title = "Histogram of College education")
ggplot(abortion_data, aes(x = collegeed, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-female}
#| warning: false
# Female
ggplot(abortion_data, aes(x = female)) +
  geom_histogram() + 
  labs(title = "Histogram of female")
ggplot(abortion_data, aes(x = female, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-unemployed}
#| warning: false
# Unemployed
ggplot(abortion_data, aes(x = unemployed)) +
  geom_histogram() + 
  labs(title = "Histogram of unemployed")
ggplot(abortion_data, aes(x = unemployed, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-ideology}
#| warning: false
# ideology
ggplot(abortion_data, aes(x = ideology)) +
  geom_histogram() + 
  labs(title = "Histogram of ideology")
ggplot(abortion_data, aes(x = ideology, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-financial}
#| warning: false
# Financial satisfaction
ggplot(abortion_data, aes(x = satisfinancial)) +
  geom_histogram() + 
  labs(title = "Histogram of Financial satisfaction")
ggplot(abortion_data, aes(x = satisfinancial, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-materialism}
#| warning: false
# WVS post-materialist index
ggplot(abortion_data, aes(x = postma4)) +
  geom_histogram() + 
  labs(title = "Histogram of WVS post-materialist index")
ggplot(abortion_data, aes(x = postma4, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-cai}
#| warning: false
# Child autonomy index
ggplot(abortion_data, aes(x = cai)) +
  geom_histogram() + 
  labs(title = "Histogram of Child autonomy index")
ggplot(abortion_data, aes(x = cai, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-trust}
#| warning: false
# Trust most people
ggplot(abortion_data, aes(x = trustmostpeople)) +
  geom_histogram() + 
  labs(title = "Histogram of whether respondent trusted most people")
ggplot(abortion_data, aes(x = trustmostpeople, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-god}
#| warning: false
# Importance of God
ggplot(abortion_data, aes(x = godimportant)) +
  geom_histogram() + 
  labs(title = "Histogram of how respondent saw God's importance")
ggplot(abortion_data, aes(x = godimportant, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-respect}
#| warning: false
# Respect for authority
ggplot(abortion_data, aes(x = respectauthority)) +
  geom_histogram() + 
  labs(title = "Histogram of respect for authority")
ggplot(abortion_data, aes(x = respectauthority, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-pride}
#| warning: false
# National Pride
ggplot(abortion_data, aes(x = nationalpride)) +
  geom_histogram() + 
  labs(title = "Histogram of National pride")
ggplot(abortion_data, aes(x = nationalpride, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

@@

We want to choose predictor variables that are not strongly correlated
with each other, are relatively balanced in our data set, and visually
appear to have a significant relationship with the outcome.

 Is there a plan B ? how to deal ? MLR compare

>>>>

```{r eda-age}
#| warning: false
#Age
abortion_data <- abortion_data %>% 
  mutate(agegroup = case_when(age >= 90 ~ '9',
                                             age >= 80  & age <= 89 ~ '8',
                                             age >= 70  & age <= 79 ~ '7',
                                             age >= 60  & age <= 69 ~ '6',
                                             age >= 50  & age <= 59 ~ '5',
                                             age >= 40  & age <= 49 ~ '4',
                                             age >= 30  & age <= 39 ~ '3',
                                             age >= 20  & age <= 29 ~ '2',
                              age <= 19 ~ '1'))
abortion_data
ggplot(abortion_data, aes(x = age)) +
  geom_histogram(binwidth = 1) + 
  labs(title = "Histogram of age")
ggplot(abortion_data, aes(x = agegroup, group = agegroup, y = aj)) +
  geom_boxplot()
```

```{r eda-college}
#| warning: false
# College education
ggplot(abortion_data, aes(x = collegeed)) +
  geom_histogram() + 
  labs(title = "Histogram of College education")
ggplot(abortion_data, aes(x = collegeed, group = collegeed, y = aj)) +
  geom_boxplot()
```

```{r eda-female}
#| warning: false
# Female
ggplot(abortion_data, aes(x = female)) +
  geom_histogram() + 
  labs(title = "Histogram of female")
ggplot(abortion_data, aes(x = female,group = female, y = aj)) +
  geom_boxplot()
```

```{r eda-unemployed}
#| warning: false
# Unemployed
ggplot(abortion_data, aes(x = unemployed)) +
  geom_histogram() + 
  labs(title = "Histogram of unemployed")
ggplot(abortion_data, aes(x = unemployed, group = unemployed, y = aj)) +
  geom_boxplot()
```

```{r eda-ideology}
#| warning: false
# ideology
ggplot(abortion_data, aes(x = ideology)) +
  geom_histogram() + 
  labs(title = "Histogram of ideology")
ggplot(abortion_data, aes(x = ideology,group = ideology, y = aj)) +
  geom_boxplot()
```

```{r eda-financial}
#| warning: false
# Financial satisfaction
ggplot(abortion_data, aes(x = satisfinancial)) +
  geom_histogram() + 
  labs(title = "Histogram of Financial satisfaction")
ggplot(abortion_data, aes(x = satisfinancial,group = satisfinancial, y = aj)) +
  geom_boxplot()
```

```{r eda-materialism}
#| warning: false
# WVS post-materialist index
ggplot(abortion_data, aes(x = postma4)) +
  geom_histogram() + 
  labs(title = "Histogram of WVS post-materialist index")
ggplot(abortion_data, aes(x = postma4, group = postma4,y = aj)) +
  geom_boxplot()
```

```{r eda-cai}
#| warning: false
# Child autonomy index
ggplot(abortion_data, aes(x = cai)) +
  geom_histogram() + 
  labs(title = "Histogram of Child autonomy index")
ggplot(abortion_data, aes(x = cai, group = cai, y = aj)) +
  geom_boxplot()
```

```{r eda-trust}
#| warning: false
# Trust most people
ggplot(abortion_data, aes(x = trustmostpeople)) +
  geom_histogram() + 
  labs(title = "Histogram of whether respondent trusted most people")
ggplot(abortion_data, aes(x = trustmostpeople, group = trustmostpeople, y = aj)) +
  geom_boxplot()
```

```{r eda-god}
#| warning: false
# Importance of God
ggplot(abortion_data, aes(x = godimportant)) +
  geom_histogram() + 
  labs(title = "Histogram of how respondent saw God's importance")
ggplot(abortion_data, aes(x = godimportant, group = godimportant, y = aj)) +
  geom_boxplot()
```

```{r eda-respect}
#| warning: false
# Respect for authority
ggplot(abortion_data, aes(x = respectauthority)) +
  geom_histogram() + 
  labs(title = "Histogram of respect for authority")
ggplot(abortion_data, aes(x = respectauthority, group = respectauthority, y = aj)) +
  geom_boxplot()
```

```{r eda-pride}
#| warning: false
# National Pride
ggplot(abortion_data, aes(x = nationalpride)) +
  geom_histogram() + 
  labs(title = "Histogram of National pride")
ggplot(abortion_data, aes(x = nationalpride, group = nationalpride, y = aj)) +
  geom_boxplot()
```

@@

We want to choose predictor variables that are not strongly correlated with each other, are relatively balanced in our data set, and visually appear to have a significant relationship with the outcome. Now that we have calculated the correlation matrix and know that some variables may have multicollinearity, we will select variables that do not exhibit significant multicollinearity for our model. Moreover, we can run several multiple linear regression models with different combinations of predictors to see which model performs best and is least affected by multicollinearity.
